A perfect storm and the natural endowments of trade-enabling infrastructure

### 2023-06-07 Slides/20min/20min.Rmd
Updated slides

---
# Descriptive evidence
![Arch](Figures/Arch_descriptive.png)
---
name: arch
**Plot of effect to the likelihood of a coin finding being generated**
![Reg_arch](Figures/arch_dummy_coins.png)
[More details](#appendixarch)

---
name: arch
**Plot of effect to the likelihood of a building finding being generated**
![Reg_arch](Figures/arch_dummy_buildings.png)
[More details](#appendixarch)

@@

**In equation form:**
- What we have: $P_i(t|c)$: Probability of $t$ given one coin 
- What we want: $P_i(\{c\}|t)$: Probability of *any* coins in time $t$
]
--
.pull-right[
### The solution
Bayes formula and Monte Carlo!
- Simple to sample from this distribution
- Sample $t$ from each coin 
- Count frequency of coin findings
]

$$P_i(\{findings\}|t)=\left[1-\prod_{c=1}^{K_i} \left( 1 - P(t|finding_c) \right)\right] P(\{findings\})$$
---
### All indicators 
![Other_ind](Figures/Arch_all.png)

>>>>

---
# Descriptive evidence
![Arch](Figures/Arch_descriptive.png)
---
name: arch1
**Plot of effect to the likelihood of a coin finding being generated**
```{r echo=FALSE, out.width="80%", fig.align='center'}
knitr::include_graphics("Figures/arch_dummy_coins.png")
```

[More details](#appendixarch); [Matched sample alternative](#matching_coins)

---
name: arch2
**Plot of effect to the likelihood of a building finding being generated**
```{r echo=FALSE, out.width="80%", fig.align='center'}
knitr::include_graphics("Figures/arch_dummy_buildings.png")
```
[More details](#appendixarch); [Matched sample alternative](#matching_buildings)

@@

**In equation form:**
- What we have: $P_i(t|c)$: Probability of $t$ given one coin 
- What we want: $P_i(\{c\}|t)$: Probability of *any* coins in time $t$
]
--
.pull-right[
### The solution
Bayes formula and Monte Carlo
- Simple to sample from this distribution
- Sample $t$ from each coin 
- Count frequency of coin findings
$$P(\{c\}|t)=\left[1-\prod_{c=1}^{K_i} \left( 1 - P(t|c) \right)\right] P(\{c\})$$
where it is assumed that
$P(t|c)\sim \mathscr{U}(Year_{min}^c; Year_{max}^c)$ or
$P(t|c)\sim \mathscr{N}(\mu_c, \sigma_c),$
$\sigma_c=\frac{(Year_{max}^c - Year_{min}^c)}{1.96}$
]

---
### All indicators 
![Other_ind](Figures/Arch_all.png)

.footnote[
[Back](#arch)
]
---
name: matching
### Soil type matching
.pull-left[
- Soil types linked to medieval developmental trajectory (Andersen et al, 2016)
- Using common soil types to estimate treatment propensity score with XGBoost 
- Soil from GEUS
- West Limfjord matched to other parishes using greedy matching. 
]

.pull-right[
*Before*
```{r echo=FALSE, out.width="80%", fig.align='center'}
knitr::include_graphics("Figures/Propensity_before.png")
```

*After*
```{r echo=FALSE, out.width="80%", fig.align='center'}
knitr::include_graphics("Figures/Propensity_after.png")
```

---
name: matching_coins
#### Coin findings (matched sample)

![Arch coins matched](Figures/arch_dummy_coins_matched.png)
[Back](#arch1)
---
name: matching_buildings
#### Building findings (matched sample)
![Arch buildings matched](Figures/arch_dummy_buildings.png)
[Back](#arch1)
---
### Safer, more convenient harbours
![Skudehandel](Figures/Wikimedia_skudehandel.jpg)
*Dangerous loading on the west coast*
